---
title: "framinghamRiskEquation"
author: 'David Fong : vkelim at bigpond dot com'
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: NULL
  md_document:
    variant: markdown_github
  html_document:
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  prettydoc::html_pretty:
    theme: cayman
    highlight: vignette
    toc: yes
    toc_depth: 4
vignette: |
  %\VignetteIndexEntry{Usage} %\VignetteEncoding{UTF-8} %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r echo = FALSE, results = 'hide', message = FALSE}
library(printr)
```

Github repository at https://github.com/DavidPatShuiFong/framinghamRiskEquation

```{r setup}
library(framinghamRiskEquation)
packageVersion("framinghamRiskEquation")
```

# Documentation

```{r}
?framinghamRiskEquation::framingham_riskequation
```

# Examples

## Example 1

This example comes from "Cardiovascular disease risk profiles" (Anderson 1991).

The worked answer in the paper is $0.22$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 1, BP = "135/80", Sex = "Female",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 230/48, Diabetes = TRUE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 5.96,
             Ethnicity = NA),
  outcome = "CHD", years = 10
)
```

The same risk-factors with outcome = "CVD" and years = 5.

The calculator on cvdcheck.org.au reports $18\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 1, BP = "135/80", Sex = "Female",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 230/48, Diabetes = TRUE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 5.96,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

The same risk-factors except Sex = "Male" with outcome = "CVD" and years = 5.

The online calculator on cvdcheck.org.au reports $20\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 1, BP = "135/80", Sex = "Male",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 230/48, Diabetes = TRUE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 5.96,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

## Example 2

This comes from "An Updated Coronary Risk Profile" (Anderson 1991).

The worked answer in the paper is $0.192$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 2, BP = "130/80", Sex = "Male",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CHD", years = 10
)
```


The same risk-factors with outcome = "CVD" and years = 5.

The online calculator at cvdcheck.org.au reports $13\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 2, BP = "130/80", Sex = "Male",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

The same risk-factors except LVH = TRUE (outcome = CVD, years = 5).

The online calculator at cvdcheck.org.au reports $21\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 2, BP = "130/80", Sex = "Male",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = TRUE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

## Example 3

This comes from "An Updated Coronary Risk Profile" (Anderson 1991)

The worked answer in the paper is $0.135$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 3, BP = "130/80", Sex = "Female",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CHD", years = 10
)
```

The same risk-factors with outcome = "CVD" and years = 5.

The online calculator cvdcheck.org.au reports $9\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 3, BP = "130/80", Sex = "Female",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA,
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

The same risk-factors except LVH = TRUE (outcome = CVD, years = 5).

The online calculator cvdcheck.org.au reports $15\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 3, BP = "130/80", Sex = "Female",
             Age = 55, SmokingStatus = "Smoker",
             CholHDLRatio = 240/45, Diabetes = FALSE, LVH = TRUE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA, 
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 6.22,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

## Example 4

This comes from "Maximising the effectiveness and cost-effectiveness of cardiovascular disease prevention in the general population" by Andrew M Tonkin, Andrew N Boyden and Stephen Colagiuri in 'Medical Journal of Australia' (191:6) 21 September 2009.

Using the provided Australian cardiovascular risk charts, the estimated risk is $5-9\%$.

The online calculator cvdcheck.org.au (with total cholesterol = 7.2, HDL 1.0) reports $9\%$.

```{r}
framingham_riskequation(
  data.frame(InternalID = 4, BP = "140/80", Sex = "Female",
             Age = 46, SmokingStatus = "Smoker",
             CholHDLRatio = 7.2, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA, 
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 7.2,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```

This example also comes from "Maximising the effectiveness and cost-effectiveness of cardiovascular disease prevention in the general population".

Using the provided Australian cardiovascular risk charts, the estimated risk is $20-24\%$.

The online calculator cvdcheck.org.au (with total cholesterol = 7.2, HDL 1.0) reports $20\%$. 

```{r}
framingham_riskequation(
  data.frame(InternalID = 4, BP = "140/80", Sex = "Female",
             Age = 66, SmokingStatus = "Smoker",
             CholHDLRatio = 7.2, Diabetes = FALSE, LVH = FALSE,
             CardiovascularDisease = FALSE, PersistentProteinuria = FALSE,
             eGFRValue = NA, eGFRUnits = NA, 
             UrineAlbuminValue = NA, UrineAlbuminUnits = NA,
             FamilialHypercholesterolaemia = NA, Cholesterol = 7.2,
             Ethnicity = NA),
  outcome = "CVD", years = 5
)
```
